Model LF

### 2022-11-30 max_dp endogen stød.Rmd
Commit

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3
macro_elas_nowage= -0.04
macro_elas_short= 0.25
macro_elas_nowage_short= -0.05
### Unemployment rate

>>>>

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3
macro_elas_nowage= -0.04
macro_elas_short= 0.28
macro_elas_nowage_short= -0.05
### Unemployment rate
